\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-07 paper.tex
need to check the last part of mcmc in related work
rewrite mcmc

Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is one most popular class that constructs a Markov chain of random transition that moves samples from an original proposed distribution to a desired distribution $ \pi (x) $.
Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important area.
Though the convergence to the desired distribution is proved to be guaranteed, the nature of random walk determines that the convergence of MCMC can be slow in a high-dimensional space.
Hamiltonian Monte Carlo(HMC)~\cite{N11} is thus introduced to reduce the random walk but directly moving to the target by heuristic.

HMC adopts physical system dynamics to propose future states in the Markov chain~\cite{N11}.
It is named ``Hamiltonian, because the concept origins from Hamiltonian dynamics, which associates the system energy with the resulting dynamics.
Define the system dynamics of an object as the position $ x $ and the momentum $ q $ over time $ t $.
We can have a system energy $ H $ of the object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
The Hamiltonian dynamics is determined by the gradients of the system energy, which is
$ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
In HMC, the state to be sampled is used as the position $ x $, and the associated probability $ P(x) $ is defined as the kinematic energy $ K(x) $.
An auxiliary variable is used as the momentum $ q $, which is associated with another probability that is defined as the potential energy $ U(q) $.
Thus, the system energy $ H(x, q) $ is associated with a joint probability $ P(x, q) $. 
As we are interested with sampling from marginal probability $ P(x) $ is interested, we will sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ as an indirect way of sampling.

The canonical distribution is often choose to bridge a system energy with a probability distribution, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
If two different states have the same energy, the probabilities of them are equivalent.
Given a target distribution $ \pi(x) $, the potential energy is defined in the form $  U(x) = - \log ( \pi(x) T ) $.

If we have of state $ x $ and define a potential energy , we can have the canonical distribution equal to $ \pi(x) $.
The collected set of $ x $ is equivalent to sampling from $ \pi(x) $.
Thus, we can use simulating the Hamiltonian dynamics to generate a set of samples from a target distribution $ \pi (x) $.
The properties of Hamiltonian dynamics guarantees so that the proposals will always be accepted, which accelerates the convergence rate.

We are going to integrate this idea into our sampling framework of efficiently generating samples under kinetic constraints. 
We define a target distribution as a uniform distribution subject to kinetic constraints and cost budgets.

>>>>

Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is one most popular class that constructs a Markov chain of random transition that moves samples from an original proposed distribution to a desired distribution $ \pi (x) $.
The random movement is driven by a jumping distribution $ g(x' \mid x) $, which samples a new state $ x' $ by a given state $ x $.
The idea of MCMC is designing a jumping distribution $ g $ that makes the desired distribution a stationary distribution $ \pi = \pi * g $.
\emph{Ergodic theorem} shows that if the jumping distribution is aperiodic, irreducible and positive recurrent~\cite{AG11}, samples generated from arbitrary distributions will gradually converge to the stationary (desired) distribution $ \pi $.
In practice, samples are initially generated from an arbitrary distribution.
They shall converge to the samples generated from the desired distribution () 
A few MCMC algorithms, e.g. Gibbs sampling and Metropolis-Hastings, have been widely used in sampling from distributions that are difficult to directly sample.

The nature of random walk in MCMC sometimes requires too many iterations to converge, especially in high-dimension state spaces.
In consider of efficiency, Hamiltonian Monte Carlo(HMC)~\cite{N11} is thus introduced to replace random walk with Hamiltonian dynamics, which means that future states in the Markov chain is proposed from simulating system dynamics instead of sampling from a jumping distribution.
It is named ``Hamiltonian, because the concept origins from Hamiltonian dynamics, which defines how system dynamics is determined by system energy.
Define the system dynamics of an object as the position $ x $ and the momentum $ q $ over time $ t $.
We have a system energy $ H $ of the object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
The Hamiltonian dynamics is determined by the gradients of the system energy, which is
$ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.

The canonical distribution is often choose to bridge a system energy with a probability distribution, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
If two different states have the same energy, the probabilities of them are equivalent.
It has been proved that properties of Hamiltonian dynamics ``leaves the canonical distribution invariant"~\cite{N11}, which means $ P(x, q) $ equals to a stationary distribution in MCMC.
Thus, we can generate samples $ [ x , q ]^T $ from joint distribution $ p(x, q) $.

Given a target distribution $ \pi(x) $, the potential energy is defined in the form $  U(x) = - \log ( \pi(x) T ) $.
We can have $ P(x, q) = \pi(x) \frac{1}{Z'} \exp ( -K(q) / T ) $, which indicates that $ pi(x) $ is a marginal distribution of $ P(x, q) $.
In HMC, we sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ so that the set of samples $ x $ equals to sampling from the marginal distribution $ \pi(x) $.
The momentum $ q $ is used as an auxiliary variable.

Thus, we can use simulating the Hamiltonian dynamics to generate a set of samples from a target distribution $ \pi (x) $.
The properties of Hamiltonian dynamics guarantees so that the proposals will always be accepted, which accelerates the convergence rate.

We are going to integrate this idea into our sampling framework of efficiently generating samples under system dynamic constraints. 
We define a target distribution as a uniform distribution subject to kinetic constraints and cost budgets.
